Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-04-19 src/tex/ms.tex
[showyourwork] overleaf sync

    \subsubsection{Chandra SNRs}
    Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}. Structures appear on multiple angular scales. This means the prior could even be learned from the data itself if sufficiently free of noise. For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}. In total we extracted \todo{insert #} patches and learned a GMM with 128 components.

@@

@@

    \subsubswction{Comparing Instruments}

>>>>

    \subsubsection{Chandra SNRs}
    Astrophysical processes forming the morphological structures are typically self-similar \todo{provide physical argument...I guess it is just the distance distribution?}. Structures appear on multiple angular scales. This means the prior could even be learned from the data itself if sufficiently free of noise. For analysis of Galactic sources with complex morphology and typically radially symmetric features such as supernova remnants (SNRs) we learned a prior from images of the bright \chandra SNRs \textit{Cas A} and \textit{G292.0+01.8}. In total we extracted \todo{insert number} patches and learned a GMM with 128 components.

@@

    \begin{figure*}
        \script{comparison-scenarios.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
            \caption{
                Comparison of different deconvolution methods for different scenarios. The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to. The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}. The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration. 
            }
            \label{fig:comparison-scenarios}
        \end{centering}
    \end{figure*}

@@

    \subsubsection{Comparing Instruments}
